\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-26 paper/mswp2012-proposal.tex
described prototyping

\subsection{User Centered Design}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

\subsection{Experimental Horizontal Prototyping}
% Software-Entwicklungsmethode
%Experimentelles Prototyping
%Erstes Ergebnis: ein erster experimenteller Prototyp
%Ziel: Sammeln von Erfahrungen mit dem Prototyp
%Bei diesem Vorgehen wird zu Forschungszwecken bzw. zur Suche nach Möglichkeiten zur Realisierung ein experimenteller Prototyp entwickelt. An diesem wird anschließend eine sehr umfangreiche Problemanalyse und Systemspezifikation durchgeführt. Die gewonnenen Erkenntnisse können anschließend in einem richtigen Produkt verwertet werden.

@@

\subsection{Empirical Study}

>>>>

\subsection{User Centered Design}
\label{subsect:ucd}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

\subsection{Experimental Horizontal Prototyping}
We decided for a combination of experimental and horizontal prototyping as software development method.

Experimental prototyping aims at creating a prototype of the system in an early phase of the development process and is therefore highly compatible with the use of user centered design (see \ref{subsect:ucd}).
There is also a connection to the empirical study part (see \ref{subsect:emp_study}), as the prototype shall be used for evaluating requirements of users as well as of partners from the industry. Not only should an early prototype lead to a higher-sophisticated user interface with respect to ui design principles and usability issues, but also provide possibility to gain results for the research part of the overall project.

The prototyping shall be executed in a horizontal manner, that means there should be a fully featured user interface before starting over with any kind of business logic implementation. The advantage of an horizontal approach is, similar to an experimental one, the perfect compatibility with user centered design. Of course this requires a strict separation of user interface and business logic implementation.

One advantage of prototyping is, that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.

% Software-Entwicklungsmethode
%Experimentelles Prototyping
%Erstes Ergebnis: ein erster experimenteller Prototyp
%Ziel: Sammeln von Erfahrungen mit dem Prototyp
%Bei diesem Vorgehen wird zu Forschungszwecken bzw. zur Suche nach Möglichkeiten zur Realisierung ein experimenteller Prototyp entwickelt. An diesem wird anschließend eine sehr umfangreiche Problemanalyse und Systemspezifikation durchgeführt. Die gewonnenen Erkenntnisse können anschließend in einem richtigen Produkt verwertet werden.

@@

\subsection{Empirical Study}
\label{subsect:emp_study}
